An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-29 VLDB2026/main.tex
Update main.tex

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

@@

	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage. Notably, PASE is evaluated exclusively on Audio, GloVe, Msong, and SIFT1M as it supports only data with dimensionality less than 512.

@@

	\textit{\textbf{Index size.}}
	%	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data. In order to unify the comparison standard, 
	%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
	To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.
	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it. To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
	As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets. This overhead stems primarily from its extensive metadata requirements. The index sizes of other methods show moderate variation. Among these, Faiss generates slightly smaller indexes due to its efficient index design.

>>>>

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{\textcolor{blue}{Index size(include original dataset)}}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

@@

	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate 3 key metrics in the single-attribute scenario: index construction time, index size, and peak memory usage. \textcolor{blue}{Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. }

@@

	\textit{\textbf{Index size.}}
	%	Traditional graph-based methods often only evaluate the size of the generated graph index and do not include the original data, while the index generated by the IVF-based method includes the original data. In order to unify the comparison standard, 
	%	we include both the index structure generated by the algorithm and the original data when evaluating the index size. 
	\sout{To ensure a fair comparison with IVF-based algorithms, we include the original dataset in the index size calculation for graph-based indexes.}
	% Traditional graph-based methods often evaluate only the size of the generated index, excluding the original data, whereas IVF-based methods include it. To ensure a consistent comparison, we consider both the index structure and the original data when measuring index size.
	As shown in the Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets. This overhead stems primarily from its extensive metadata requirements. The index sizes of other methods show moderate variation. Among these, Faiss generates slightly smaller indexes due to its efficient index design.
